---
title: "ggplot2 mlmRev"
output: html_document
---

```{r setup, echo=FALSE}
library(knitr)
library(mlmRev)
library(tidyverse) # will get ggplot2
```
## data from package ‘mlmRev’

Mmmec data set
Malignant  Melanoma  Mortality  in  the  European  Community  associated  with  the  impact  of  UVradiation exposure.

Column names:
```{r Mmmec col names, echo=FALSE}
names(Mmmec) 
```
2 rows from head:
```{r Mmmec head-2, echo=FALSE}
head(Mmmec, 2)
```
Data summary:
```{r Mmmec summary, echo=FALSE}
summary(Mmmec)
```
Histogram:
```{r histgg mmmec, echo=FALSE}
ggplot(Mmmec, aes(x=deaths)) + geom_histogram()
```

Histogram with adjustments:
```{r histgg mmmec, echo=FALSE}
ggplot(Mmmec, aes(x=deaths)) + geom_histogram(binwidth = 20,
            fill="white",colour="black")
```

```{r bar6 uvb mmmec, echo=FALSE}
ggplot(Mmmec, aes(x=nation, y=deaths)) + 
       geom_bar(stat = "identity") # heights of the bars represent values in the data
```

Points, scatterplot for aech country number od deaths:
```{r sc1 mmmec, echo=FALSE}
ggplot(Mmmec, aes(x=deaths, y=nation)) + 
       geom_point(color='darkblue')
```

Violin plot:
```{r sc2 mmmec, echo=FALSE}
ggplot(Mmmec, aes(x=nation, y=deaths)) + 
       geom_violin()
```

UV radiation exposure in each country
```{r sc3 uvb mmmec, echo=FALSE}
ggplot(Mmmec, aes(x=deaths, y=nation)) + 
       geom_point(aes(color=uvb))
```

```{r sc4 uvb mmmec, echo=FALSE}
ggplot(Mmmec, aes(x=deaths, y=nation)) + 
       geom_point(aes(color=uvb, size=nation))
```

Deaths in Belgium and Italy and uvb exposure
```{r deaths uvb in 2 countries mmmec, echo=FALSE}
ggplot(filter(Mmmec, nation %in% c("Belgium","Italy")),
              aes(x=deaths, y=uvb, color=nation)) + 
              geom_point()
```

```{r uvb deaths in 2 countries mmmec, echo=FALSE}
ggplot(filter(Mmmec, nation %in% c("Belgium","Italy")),
              aes(x=uvb, y=deaths,
              color=nation)) + geom_point()
```

France and Italy
```{r uvb deaths in Fr It mmmec, echo=FALSE}
ggplot(filter(Mmmec, nation %in% c("France","Italy")),
              aes(x=uvb, y=deaths, color=nation)) + 
              geom_point()
```

geom_text 
```{r uvb deaths in 2 countries text, echo=FALSE}
ggplot(filter(Mmmec, nation %in% c("Denmark","Luxembourg")),
              aes(x=uvb, y=deaths, color=nation)) + 
                geom_point() +
                geom_text(aes(label=region), size = 6)
```

in regions in France 
```{r uvb deaths region, echo=FALSE}
ggplot(filter(Mmmec, nation %in% c("France")),
              aes(x=uvb, y=deaths, color=nation)) + 
                geom_point(aes(color=region)) 
```

in regions of Luxembourg
```{r uvb deaths Lux region, echo=FALSE}
ggplot(filter(Mmmec, nation %in% c("Luxembourg")),
              aes(x=uvb, y=deaths, color=nation)) + 
                geom_point(aes(color=region, shape=county)) 
```

Luxembourg and Danmark 
```{r uvb deaths in 2 ggrepel, echo=FALSE}
library(ggrepel)
ggplot(filter(Mmmec, nation %in% c("Denmark","Luxembourg")),
              aes(x=uvb, y=deaths, color=nation)) + 
                geom_point() +
                geom_text_repel(aes(label=region), size = 6)
```


```{r uvb deaths Den Lux, echo=FALSE}
ggplot(filter(Mmmec, nation %in% c("Denmark","Luxembourg")),
              aes(x=uvb, y=deaths)) + 
                geom_point(aes(color=nation, size=deaths)) 
```



