---
title: "tigerstats package"
output: html_document
---

```{r setup, echo=FALSE}
library(knitr)
library(tigerstats)
library(tidyverse)
#library(ggplot2)
```
## data from package ‘tigerstats’, (Dec 2016)

imagpop dataset - imaginary population
Dataset dimention, column names, dataset structure:
```{r imagpop, echo=FALSE}
dim(imagpop)
names(imagpop)
str(imagpop)
summary(imagpop)
```

head
```{r head imagpop, echo=FALSE}
head(imagpop)
```
Base graphics histogram
```{r hist imagpop, echo=FALSE}
hist(imagpop$income)
```

ggplot2 histogram:
```{r histgg imagpop, echo=FALSE}
ggplot(imagpop, aes(x=income)) + geom_histogram()
```

```{r two_geoms imagpop, echo=FALSE}
ggplot(imagpop, aes(x=income, y=height ,color=sex)) +
  geom_point() + geom_smooth()
```

```{r one_geoms imagpop, echo=FALSE}
  ggplot(imagpop, aes(x=height, y=income, color=sex)) +
  geom_point() +
```

specifying the aesthetics inside the geoms
```{r aes_in_geoms imagpop, echo=FALSE}
ggplot(imagpop) + 
         geom_point(aes(x=income, y=height ,color=sex)) +
         geom_smooth(aes(x=income, y=height ,color=sex)) 
```

Opinion of death panalty by gender:
```{r bar cappun gender, echo=FALSE}
ggplot(imagpop, aes(x=cappun, fill=factor(sex))) +
  geom_bar(stat="count", position="fill") +
  scale_fill_brewer(palette="Paired")
```

Opinion of death panalty by income:
```{r bar cappun income, echo=FALSE}
ggplot(imagpop, aes(x=income, fill=factor(sex))) +
  geom_bar(stat="count", position="fill") +
  scale_fill_brewer(palette="Set1")
```

Opinion of death panalty by gender and income:
```{r cappun 2 gender income, echo=FALSE}
ggplot(imagpop, aes(x=cappun, y=income ,color=sex)) +
  geom_area()
```

View on capital punnishment by income and gender
```{r cappun 3 gender income, echo=FALSE}
ggplot(imagpop)+
  geom_boxplot(aes(x=cappun, y=income, fill=sex))+
  scale_fill_brewer(palette="Dark2")
```

Violin plot:
```{r cappun 4 gender income, echo=FALSE}
ggplot(imagpop)+geom_violin(aes(x=cappun,y=income,fill=sex))+
  scale_fill_brewer(palette="Set2")
```

```{r cappun 5 gender income, echo=FALSE}
ggplot(imagpop)+geom_col(aes(x=cappun,y=income,fill=sex))+
  scale_fill_brewer(palette="Accent")
```
Math and income 
```{r cappun 6 gender income, echo=FALSE}
ggplot(imagpop)+geom_bar(aes(x=height, y=income, fill=math),stat='identity') + 
  scale_fill_brewer(palette="Set2")
```

```{r jitter1, echo=FALSE}
cbPalette=c("blue","orange") # manual color setting
ggplot() +
     geom_jitter(data=imagpop, aes(math, income, colour = factor(sex)))+
     scale_color_manual(values=cbPalette)
```

Math, height, cappun
```{r jitter2, echo=FALSE}
cbPalette=c("blue","orange") # manual color setting
ggplot() +
    geom_jitter(data=imagpop, aes(math, height, colour = factor(sex)))+
    facet_grid(cappun ~ .) +
    scale_color_manual(values=cbPalette) +
    theme_dark()
```

Math, income, cappun
```{r jitter3, echo=FALSE}
myPalette=c("darkgreen","violet")
ggplot(imagpop) +
    geom_jitter( aes(math, income, colour = factor(sex)))+
    facet_grid(cappun ~ .)+ 
   scale_color_manual(values=myPalette) +
    theme_linedraw()
```

```{r jitter4, echo=FALSE}
ggplot(imagpop) +
    geom_jitter( aes(cappun, income, colour = factor(sex)))+
    facet_grid(math ~ .)+
    scale_color_hue(l=30, c=55)+
    theme_linedraw()
```

```{r jitter5, echo=FALSE}
ggplot(imagpop, aes(x=cappun, y=income, factor=sex)) + 
  geom_boxplot(notch = TRUE)+
  geom_jitter(position=position_jitter(0.1))
```

```{r jitter6, echo=FALSE}
ggplot(imagpop, aes(x=cappun, y=income, color=sex)) + 
  geom_jitter(position=position_jitter(0.4))
```

library(tigerstats)
dataset nonresponse - non-response to a mail survey in Demnark
Basic info: dimention, names of colomns, head
```{r nonresponse dataset, echo=FALSE}
dim(nonresponse)
names(nonresponse)
head(nonresponse,2)
```

Histogram - residence: in Copenhagen, or a city outside of Copenhagen, or in thecountryside:
```{r hist1 nonresponce, echo=FALSE}
ggplot(nonresponse, aes(x=residence)) + geom_histogram(stat="count")
```

Histogram - residence:
```{r hist2 nonresponce, echo=FALSE}
ggplot(nonresponse, aes(x=residence)) + 
  geom_histogram(binwidth = 10,
  fill="gray",colour="black", 
  stat="count")
```

Histogram - gendeer:
```{r hist3 nonresponce, echo=FALSE}
ggplot(nonresponse, aes(x=gender)) + 
  geom_histogram(binwidth = 10,
  fill="violet",colour="black", 
  stat="count")
```

```{r j, echo=FALSE}
ggplot(nonresponse) +
    geom_jitter( aes(gender,response, colour = factor(residence)))+
    theme_linedraw()
```


```{r j2, echo=FALSE}
myPalette=c("darkgreen","violet", "blue")
ggplot(nonresponse) +
    geom_jitter( aes(gender,response, colour = factor(residence)))+
   # facet_grid(gender ~ .)+ 
   scale_color_manual(values=myPalette) +
    theme_linedraw()
```

```{r j3, echo=FALSE}
myPalette=c("darkgreen","purple", "blue")
ggplot(nonresponse) +
    geom_jitter( aes(gender, response, colour = factor(residence)))+
   facet_grid(residence ~ .)+ 
   scale_color_manual(values=myPalette) +
    theme_linedraw()
```

deathpen dataset:
Number of capital cases in Florida in 1976-1977 vs race of defendent and victim
Dataset sescription: dimention, column names, head
```{r descr, echo=FALSE}
dim(deathpen)
names(deathpen)
head(deathpen,2)
```
Race of the defendent
```{r hist_race, echo=FALSE}
ggplot(deathpen, aes(x=defrace)) + 
  geom_histogram(binwidth = 10,
  fill="purple",colour="black", 
  stat="count")
```

Race of the victim
```{r hist_race, echo=FALSE}
ggplot(deathpen, aes(x=vicrace)) + 
  geom_histogram(binwidth = 10,
  fill="purple",colour="black", 
  stat="count")
```


Defendent race vs death or not
```{r bar def race d, echo=FALSE}
ggplot(deathpen, aes(x=defrace, fill=factor(death))) +
  geom_bar(stat="count", position="fill") +
  scale_fill_brewer(palette="Set2")
```

Victim race vs death or not
```{r bar def race d, echo=FALSE}
ggplot(deathpen, aes(x=vicrace, fill=factor(death))) +
  geom_bar(stat="count", position="fill") +
  scale_fill_brewer(palette="Set2")
```

tornado dataset showing tornado damage
```{r tornado, echo=FALSE}
dim(tornado)
head(tornado)
```

Data summary
```{r structure, echo=FALSE}
summary(tornado)
```

Annual tornado damage > $50 mln
```{r dam50, echo=FALSE}
ggplot(filter(tornado, damage > 50),
    aes(x=state, y=damage))+
     geom_bar(stat='identity')
```

Damage < $0.3 mln, Dec 2016
```{r filter damage, echo=FALSE}
ggplot(filter(tornado, damage < 0.3),
       aes(state,damage))+geom_bar(stat='identity')
```

Puerto Rico vs Nevada -  data from late 2016 
```{r PuertoRico Nevada, echo=FALSE}
tornado %>% filter(state == 'PuertoRico' | state == 'Nevada') %>%
  ggplot(aes(state,damage)) + geom_bar(stat='identity')
```

States starting with P
```{r P echo=FALSE}
tornado %>% filter(str_detect(state,'^P')) %>%
  ggplot(aes(state,damage)) + geom_bar(stat='identity')
``` 
  
States containing 'north' 'south' - partial matching
```{r partial matching echo=FALSE}
tornado %>% filter(str_detect(state,"North|South")) %>%
  ggplot(aes(state,damage)) + geom_bar(stat='identity')
``` 