---
title: "lattice_mlmRev_other"
output: html_document
---

```{r setup, echo=FALSE}
library(knitr)
library(mlmRev)
library(lattice)
```
## data from package ‘mlmRev’

'bdf' data frame -  language  scores  from  grade  8  pupils  inelementary schools in The Netherlands:
head - first 6 rows:
```{r bdf package head, echo=FALSE}
head(bdf)
```
bdf data frame dimention, structure, summary:
```{r bdf dim, echo=FALSE}
dim(bdf)
str(bdf)
```

Data frame dimention, structure, summary:
```{r bdf summary, echo=FALSE}
summary(bdf)
```
Histogram of socioeconomic status of the pupils:
```{r ses_hist, echo=FALSE}
library(lattice)
histogram(~ ses, data = bdf)
```
Histogram of sex of the students:
```{r sex_hist, echo=FALSE}
library(lattice)
histogram(~ sex, data = bdf)
```
Barchart of socio econ stat, gender & langPRET
```{r sex_barchart, echo=FALSE}
barchart(ses ~ langPRET | sex, bdf)
```
Dotplot
```{r sex_dotplot1, echo=FALSE}
dotplot(ses ~ langPRET | sex, bdf)
```

```{r sex_dotplot2, echo=FALSE}
 dotplot( langPRET ~ ses, data = bdf, groups = sex, type = "o",
auto.key = list(space = "right", points = TRUE, lines = TRUE))
```

```{r xyplot1, echo=FALSE}
 xyplot(ses ~ langPRET, data=bdf)
```


```{r xyplot2, echo=FALSE}
xyplot(ses ~ langPRET, data=bdf, scales = list(log = TRUE),
type = c("p", "g", "smooth"))
```

```{r sex_barchart2, echo=FALSE}
barchart(ses ~ IQ.verb | sex, bdf)
```

egsingle data set - mathematics score
```{r egsingle info, echo=FALSE}
dim(egsingle)
names(egsingle)
```

Year of the test ~ student's grade
```{r hist1, echo=FALSE}
histogram(year ~ grade | factor(female), data=egsingle)
```

```{r histo2, echo=FALSE}
histogram(~ grade | factor(year), egsingle, groups=female)
```


```{r dp1, echo=FALSE}
densityplot(~ year | factor(female), egsingle, groups=grade,
            plot.points=FALSE, auto.key=TRUE)
```

```{r dp2, echo=FALSE}
densityplot(~ grade | factor(year), egsingle, groups=female,
            plot.points=FALSE, auto.key=TRUE)
```

```{r histo3, echo=FALSE}
histogram(~ grade | factor(black), data=egsingle)
```

```{r bar_gender, echo=FALSE}
barchart(year ~ grade | female, egsingle, layout = c(2,1), origin=0)
```

```{r bar_black, echo=FALSE}
names(egsingle)
barchart(year ~ grade | black, egsingle, layout = c(2,1), origin=0)
```

```{r bar_spanic, echo=FALSE}

barchart(year ~ grade | hispanic, egsingle, layout = c(2,1), origin=0)
```
box-and-whisker plot
```{r bw_, echo=FALSE}
bwplot(year ~ female | factor(black), egsingle, layout = c(2,1))
```


```{r xy info, echo=FALSE}
xyplot(grade ~ female | retained, data = egsingle, layout=c(4,1))

```

```{r xy scatter, echo=FALSE}
xyplot(female ~ grade, data = egsingle, grid=TRUE,
       abline = c(0,1))
```
Mmmec data set
Malignant  Melanoma  Mortality  in  the  European  Community  associated  with  the  impact  of  UVradiation exposure
```{r Mmmec description, echo=FALSE}
dim(Mmmec)
names(Mmmec)
str(Mmmec)
```
Data set summary:
```{r Mmmec summary, echo=FALSE}
summary(Mmmec)
```

```{r hist_nation, echo=FALSE}
histogram(~ nation, data=Mmmec)
```
Deaths among men in 9 countries
```{r xyplot_mmmec, echo=FALSE}
xyplot(nation ~ deaths, data=Mmmec)
```

```{r head_mmec, echo=FALSE}
head(Mmmec)
```

Color by nation
```{r xyplot_tri, echo=FALSE}
xyplot(uvb ~ deaths, group=nation ,data=Mmmec, auto.key = TRUE)
```

Multiple panels by group
```{r xyplot_panels, echo=FALSE}

xyplot(uvb ~ deaths | nation,
       group=nation, data = Mmmec, 
      # type = c("p", "smooth"),
       scales = "free")
```

Cloud - 3D
```{r cloud1, echo=FALSE}
cloud(uvb ~ uvb * deaths,
       group=nation, data = Mmmec, 
       auto.key = TRUE)
```
```{r cloud2, echo=FALSE}
cloud(uvb ~ uvb * deaths,
       group=nation, data = Mmmec)
```

```{r 3D, echo=FALSE}
cloud(deaths ~ deaths * uvb,
       group=nation, data = Mmmec)
```

