---
title: "R downloads data"
from: "1/10/2019"
output: html_document
---
## Expert Data Analysis with R
```{r ustawienia, echo=FALSE, results='hide'}
library(dplyr)
library(EDAWR)
library(data.table) 
library(R.oo)
library(R.utils) # needed for fread()
```
Loading the file using fread function:
```{r file_load, echo=FALSE, results='hide'}
df <- fread('~/Documents/R/Rdatafiles/2019-10-01-r.csv.gz')
```
tbl_df function - a kind of data frame 
```{r tibble, echo=FALSE}
tbl <- tbl_df(df) 
```
```{r data dimention, echo=FALSE}
dim(tbl) 
```
Grouping data, printing head
```{r group_by, echo=FALSE}
  by_country <- group_by(tbl,country)
  by_country
```
Summarizing
```{r summary, echo=FALSE}
   pack_sum <- summarize(by_country, count = n(), 
	 unique=n_distinct(ip_id), countries=n_distinct(country))
   pack_sum
```
Data structure:
```{r structure, echo=FALSE}
   str(pack_sum)
```
count median
```{r median of count variable, echo=FALSE}
median(pack_sum$count, na.rm=TRUE)
```
unique median
```{r median of unique variable, echo=FALSE}
median(pack_sum$unique, na.rm=TRUE)
```
count mean
```{r mean of count variable, echo=FALSE}
mean(pack_sum$count, na.rm=TRUE)
```
count mean
```{r mean of unique variable, echo=FALSE}
mean(pack_sum$unique, na.rm=TRUE)
```
quantile
```{r quantile of count, echo=FALSE}
quantile(pack_sum$count)
```
Top counts of R downloads per country
```{r top counts, echo=FALSE}
top_counts <- filter(pack_sum, count > 11)
top_counts
```
Sorted top counts
```{r sorted, echo=FALSE}
top_counts_sorted <- arrange(top_counts, desc(count))
top_counts_sorted
```
quantile of uniques:
```{r quantile, echo=FALSE}
quantile(pack_sum$unique)
```
Top unique - downloads from 1 computer counted as 1
```{r uniques sorted, echo=FALSE}
top_uniques <- filter(pack_sum, unique > 15)
top_uniques_sort <- arrange(top_uniques, desc(unique)) 
top_uniques_sort
```
On October 1st 2019 there were total of 2922 downloads of R programming language, or 1348 by individual users. The top country from which downloads were recorded was US, second was Great Britain, third was Japan.
